Fisheries management when quotas are costly to change

### 2014-08-06 manuscripts/presentation.Rmd
self-contained with printing

---
title: "Fisheries management when quotas are costly to change"
date: "08/12/2014"
output: 
  revealjs_presentation:
    theme: serif
    self_contained: false
    incremental: true
    transition: none
    pandoc_args: ["--css", "components/style.css"]
author: Carl Boettiger, Michael Bode, James Sanchirico, Jacob LaRiviera, Alan Hastings, Paul Armsworth

@@

## Bluefin Tuna Stocks vs US Quota, ICCAT 1987 - 2007

@@

>>>>

---
title: "Fisheries management when quotas are costly to change"
date: "08/12/2014"
output: 
  revealjs_presentation:
    theme: serif
    self_contained: true
    incremental: true
    transition: none
    pandoc_args: ["--css", "components/style.css"]
author: Carl Boettiger, Michael Bode, James Sanchirico, Jacob LaRiviera, Alan Hastings, Paul Armsworth

@@

## Bluefin Tuna Stocks vs Quota (base TAC), ICCAT 1987 - 2007

@@

<small> base TAC for the stock (before any underages or overages are applied or divided by country)</small>
